\section{The Housing Crisis}

There are three basic necessities that are essential to human survival:

\begin{enumerate}
\item A nutritionally balanced diet
\item Access to quality health care
\item Adequate shelter from the elements
\end{enumerate}

Without all three of those basic necessities, a human can not thrive and the average lifespan is significantly reduced. Without all three of those basic necessities, upward class mobility is virtually impossible.

The \textbf{Declaration of Independence} explicitly states:

\begin{quote}
{\fontfamily{pzc}\selectfont\large%
We hold these truths to be self-evident, that all men are created equal, that they are endowed by their Creator with certain unalienable Rights, that among these are Life, Liberty and the pursuit of Happiness.}
\end{quote}

The founding fathers proclaimed that life, liberty, and the pursuit of happiness are unalienable \emph{(unable to be taken away from or given away by the possessor)} rights. Those rights are only possible when the opening three basic necessities are met.

The red rose did not exist in 1776. The Socialist Labor Party of America was founded in 1876 but I believe the red rose really did not definitively exist in America (my subjective opinion) until 1912\footnote{\url{https://bit.ly/33MUNCY}}. Yet what I see there in the Declaration of Independence is a pretty close match to how I define socialism. Life and Liberty easily equate with human dignity and autonomy---and the pursuit of happiness is a good match for opportunity of upward class mobility.

Note I am \emph{not} claiming our founding fathers were socialist. Their acts of genocide against Indigenous Peoples and their implementation and protection of the institution of slavery clearly are both in opposition to core socialist principles. But were it not for their bigoted Western European ethnic and cultural supremacy world views, they very well may have been headed on the right path. Bigotry seems to ruin everything. Bigotry produces elitism and classism---bigotry and capitalism thus go hand in hand and I suggest (academic research still needed) bigotry always leads to fascism, as happened in Germany and as is happening here in America as I type.

Despite the fact that our founding fathers very clearly specified that life, liberty, and the pursuit of happiness are unalienable rights---the three basic necessities required to have those rights in the United States of America have become the subject of capitalist monetization rather than the subject of a socialist safety net. Those three basic necessities must be \emph{purchased with capital} providing profit for the hoarder of those necessities.

What happens when a person does not have the available capital to pay for all three of those resources? Something has to give way.

It is my \emph{anecdotal personal} experience that the first to give way is access to quality health care. You start seeing the doctor less often. You may still technically have health insurance, but you avoid seeing the doctor when you should because the copay is too high and you fear the cost of prescriptions you can not afford. As poverty increases, a nutritionally balanced diet starts to become difficult to afford, increasing the need for the health care that you can not afford. Finally, adequate shelter from the elements becomes too costly and you become homeless.

This cycle is hastened by a housing market that is not by any stretch of the imagination a fair market. In California in 1968 a minimum wage earner took home \money{1.65} an hour. If that worker worked full time, that provided a monthly income of about \money{277.20} a month. The median rent, including utilities, was about \money{108} in 1970. Less than half of the gross income of a minimum wage employee went to obtaining adequate protection from the elements.

Just fifty years later in 2020, the median rent is about \money{1100} a month. It would take a federal minimum wage of just over \$13.00 an hour for only half of a full-time minimum wage job to cover that, yet the federal minimum wage is only \money{7.25} an hour, providing a gross income of only \money{1218} a month.

During the last fifty years, the cost of housing in the United States has skyrocketed compared to the wages paid to the poor.

\subsection{The Sin of Gentrification}

Gentrification is the process by which those of a lower economic class are forced out of a community by those of a higher economic class moving in.

At its heart, gentrification is the culmination of the capitalist philosophy that those who have more financial resources are inherently of a higher value than those who have less financial resources. That capitalist philosophy encourages exploitation because how the financial resources were gained is not relevant---only that they were gained. The love of money truly is at the root of all things that are evil, including gentrification.

Gentrification denies the poor class of the Life, Liberty, and Pursuit of Happiness that the Declaration of Independence \emph{so clearly} defines as unalienable rights. For those who seek religious authority, the Declaration of Independence goes as far as declaring those rights to be endowed upon us by our Creator. For those who seek religious authority, that makes gentrification a sin against God and not just a sin against society.

Gentrification is also part of the systemic racism that plagues this country. The poor are not restricted to people of color, but statistically speaking you are far more likely to live in poverty if you are not white than if you are white and if you are poor and white, class mobility out of poverty is much easier than if you are poor and not white.

The causes of gentrification are many and not all are well-understood. Three of them follow.

\subsubsection{Redlining}

By its strictest definition, the practice of redlining took place from the 1930s to the late 1960s\footnote{\url{https://bit.ly/3hGLc90}}.

Under the practice, banks would \emph{use federal guidelines} from a \textbf{government sponsored corporation} called the ``Home Owners' Loan Corporation'' to define certain neighborhoods as too risky for a mortgage. Such classification was largely based upon the ethnic makeup of the community.

This resulted in poor minority homeowners being unable to obtain the home loans they needed to keep their home in good repair and it prevented prospective home owners from being able to obtain a loan resulting in a loss of value.

The only options those seeking loans had was to procure a loan from a predatory lender or for existing homeowners who did not want a predatory loan, allow the home to fall into disrepair. When a loan was procured from a predatory lender, foreclosure often resulted with the home then being sold to a slumlord who rented it without proper maintenance being performed on the home.

Redlining was a direct result of Franklin D.\ Roosevelt's `New Deal' that many liberals love to praise. The `New Deal' was good for white Americans but many aspects of it contributed to the systemic racism this nation still is quite guilty of. Any policy intended to help the poor \emph{MUST} undergo frequent review to make sure it is actually helping those it is intended to help \emph{especially} looking at whether minorities are benefiting or being hurt by the policy.

Even though redlining is no longer practiced, the impacts of redlining are still very prevalent.

It is the opinion of the Anymouse Prophet that while the strict definition of redlining is no longer practiced, the financial industry now uses credit rating to accomplish the same goal and I suspect that was an intentional motivation in the creation of the credit rating system.

Redlining is directory responsible for some communities falling into such disrepair that many of the houses are no longer livable and end up being used for drug cooking. This in turn inspired privileged white mayors like South Bend mayor Pete Buttigieg who bulldoze houses in his `\num[group-separator={,}]{1000} houses in \num[group-separator={,}]{1000} days' gentrification plan\footnote{\url{https://bit.ly/2T3ou0C}} that resulted in housing too expensive for minorities and thus directly reduced the ethnic and financial diversity of South Bend.

Pete Buttigieg did concede---while he was attempting to get the DNC Presidential nomination---that the decision was a bad one and he claimed he did not realize gentrification would result.

I believe he is lying. If he isn't lying then it was extreme incompetence but he is a very intelligent and well-educated man so I find that unlikely. As mayor, it was his job to know the probable impact and in an Internet age, there is no question he had the resources to do the research and see what would result.

Note that this man---either a liar or severely incompetent---is now the United States Secretary of Transportation, likely a position he acquired in a deal with the DNC to pledge his delegates to Joe Biden when it looked like Bernie Sanders had a real chance at the nomination\footnote{\url{https://bit.ly/3fzJQdl}}. The game of `3D Chess' our capitalist oligarchy likes to play is never about what is best for the working class.

The practice and impact of redlining teaches us two \emph{very} important lessons:

\begin{enumerate}
  \item Policies such as the `New Deal' often hailed as progressive and constructive by white `Liberals' frequently include \emph{intentional} systemic racism against minorities.
  \item Bad policies can have a \emph{very long} impact lasting many decades after the policy has ended. It is therefore critical to frequently analyze the impact of any policy as objectively as possible to both make sure the intended outcome is in fact happening and to make sure that when it does appear to be working, it is working for minorities and the poor and not just the white middle and wealthy classes.
\end{enumerate}

We must be willing to accept that sometimes something does not work no matter how passionately or badly we want it to work. The only way to really know if something works is through an objective analysis of the impact. Doing an objective analysis is critical for every policy we pass both before and after it passes. We must avoid policies that continue to do harm decades after we halt their implementation. We must catch those flawed policies as early as possible.

\subsubsection{Corporate Retail Discrimination}

The city of Brentwood, California (different than the Los Angeles suburb) until recently was primarily orchard and farmland. As a child, we use to travel to Brentwood from the west county to buy crates of peaches from the orchards that my mother would then can to last us most of the year. Brentwood also produced really good sweet corn\footnote{\url{https://bit.ly/3yq9Sss}}, and still does though not in the same quantity. As such there is a large Hispanic community in Brentwood that either are agricultural workers are are descendant from them.

During the housing boom at the beginning of the century, many McMansion\footnote{\url{https://bit.ly/3bGFPTw}} communities were built on former agricultural land in Brentwood. These McMansions were out of the price range of the majority of people living in Brentwood at the time and brought in a lot of financially privileged families who had good paying jobs in San Francisco or Silicon Valley and were willing to commute.

To give these new residents a place to spend their money locally, in 2008 the `Streets of Brentwood' shopping center was built, designed to give a similar feeling of elegance as you might find in Walnut Creek with the exception that everything is flat in Brentwood. Brentwood is a former floodplain for the Sacramento and San Joaquin river delta, which is why it makes such good farmland and it really is a shame that so much of it has been turned into a field of McMansions. I suppose slash and burn agricultural clearing in South America is where a lot of our food now comes from---and that is an exploitative capitalist tragedy of a different kind.

Back on topic, a major high-end clothing retailer I will not mention because I do not wish to be buried in frivolous lawsuits was committed to opening a retail location in the `Streets of Brentwood'.

Low-income renters in Brentwood had concerns that rents were going to increase as a result of `Streets of Brentwood' so to their credit the city council agreed to build additional low income housing not too far from the `Streets of Brentwood'. From a logistics perspective this actually makes sense---such a shopping center depends upon the working class to staff the shops the financially privileged will shop at and so they need an affordable place to live.

The previously un-named major high-end clothing retailer however did not like the fact that there would be low-income housing within a certain proximity of their retail location, so they pulled out of the `Streets of Brentwood' and decided not to open there. I have a suspicion that some other existing retailers there pulled out for the same reason, though they may have left because of the recession.

If you want to shop at this particular high-end clothing retailer, Walnut Creek where there is not much in the way of low-income housing I believe is their closest location to Brentwood.

This same kind of thing happens all over this country and not just with clothing retailers. It is also a driving factor behind food deserts\footnote{\url{https://bit.ly/3yn4Dto}}.

Large corporations put pressure on cities \emph{not} to build low-income housing. Cities with low-income housing do not get these profit generating retailers and as such they do not profit from the tax revenue generated by these retailers. Money spent by the financially privileged residents of cities that also provide low-income housing ends up being spent in \emph{other} cities that do not provide low-income housing and those cities profit from the tax revenue.

The low-wage employees then have to commute considerable distances from where they live just to staff these locations, reducing their opportunity for education and self-improvement. And when these low-wage employees lose their job to automation, their local city has fewer resources to help them because the tax revenue is going to the cities that do not provide low-income housing. Also, these cities that are basically blacklisted by many corporations because of their low-income housing have less money for city maintenance in general.

Corporate America literally encourages gentrification by withholding business from cities and towns that don't gentrify and drive out their poor. Capitalism---driven by a love of money---\emph{inherently} drives gentrification as explained in a passage from Ecclesiastes 5 that Capitalist Evangelicals like to ignore:

\begin{quote}
If you see the poor oppressed in a district, and justice and rights denied, do not be surprised at such things; for one official is eyed by a higher one, and over them both are others higher still. The increase from the land is taken by all; the king himself profits from the fields. \hl{Whoever loves money never has enough; whoever loves wealth is never satisfied with their income.}
\end{quote}

It is this continual seeking of additional wealth by those who already have wealth that is at the root of the oppression of the poor, including the oppression of gentrification.

Checks and balances \textbf{MUST} be put into place to prevent this, for where there are none, the oppression will continue until the poor have nothing left to live for. And when the poor have nothing left to live for, we will look for a cause to die for, and the streets will flow with blood like they did during the French Revolution and the `reign of terror'\footnote{\url{https://bit.ly/3u3dxci}}. I would very much like to avoid that.

The `The Thirty-Five Percent Plan' detailed starting on page~\pageref{thirtyfive} does not directly address this issue as a check and balance but it does provide some incentive for cities to make sure there is adequate low-income housing and it also provides some incentive for businesses to locate where there is adequate low-income housing.

I think to address this issue of corporate discrimination there needs to be an incredibly stiff tax penalty on retail corporations that choose where retail locations are opened based upon the kind of housing near the retail locations. Make such discrimination expensive and the incentives to open locations where there is low-income housing become even more attractive.

\subsubsection{Over-building and White Flight}

During the first decade of this century, for the financially privileged, new housing actually outpaced demand. For the poor, housing was not built to meet demand.

This inequality in the housing market is largely responsible for what many term as \textbf{\textit{White Flight}}---Financially privileged white people abandoning a community that previously had decent diversity to move to new housing they can afford, resulting in their former community becoming largely minority with decreased housing values.

I witnessed this happen during that decade in Antioch, California when many of the McMansions in Brentwood were built during that housing boom. Many of the older communities that actually had a decent amount of ethnic and economic diversity in them suddenly saw a lot of the middle class white families leave to buy the new McMansions in Brentwood. Those older Antioch communities (as well as older Brentwood communities) saw a marked increase in their Hispanic and Black working class demographics as the white middle class residents left.

The children in those middle class families that moved out proceeded to grow up in the largely white McMansion communities with far less exposure to actual ethnic and cultural diversity (though not completely without such exposure, the San Francisco Bay Area is still pretty diverse) and many of the small businesses in the older communities in Antioch they moved out of had to move or close because the communities became too poor---especially during the recession of 2008---to support those businesses.

The quality of the public schools in those older Antioch communities also declined as funding for schools largely comes from property taxes.

The `White Flight' that I witnessed in those Antioch communities was just one instance, the same thing happens from time to time in many parts of the country.

As I see it, `White Flight' causes two different problems:

\begin{enumerate}
  \item It reduces ethnic and cultural diversity, leading to segregated communities. People often fear what they do not know and are easily persuaded to hate what they fear. We (myself included) like to cite Donald Trump and the `alt-right' for increasing racial tensions but I suspect a large part of the blame may actually belong with `White Flight' that happened as a result of the housing boom at the beginning of this century.
  \item While it is true that housing within the community middle class white people are fleeing from becomes more affordable to working class minorities, the community itself becomes poorer which opens the community up to increased crime and potential gentrification where people in the community become homeless and the community is then gentrified for higher income buyers. It may take decades to happen but just like what Pete Buttigieg did in South Bend, too often it is the ultimate result.
\end{enumerate}

The only way to solve the ethnic diversity problem of `White Flight' is to end the systemic racial economic inequality that is very real in this country. That way when there is a new housing community that is attractive to the middle class, ethnic and cultural diversity is maintained in the new housing community because the middle class itself is ethnically and culturally diverse.

Raising the minimum wage to an actual \emph{livable} wage is a very important part of that process. Ending police discrimination---the very thing Colin Kaepernick peacefully protested for---is also critical to fixing the systemic racial economic inequality. Education in economically depressed communities \emph{must} be improved. This means a reduction in class size, increasing teacher wages, and increasing funds for extra-curricular activities such as music, performing arts, and non-performing arts. As Helen M.\ Todd put it: ``The Roses of life: music, education, nature, and books---shall be the heritage of \emph{every} child that is born in the country\ldots{}''

Unpaid internships need to be outlawed. Unpaid internships are often very valuable on the resume but only those born into families of financial privilege can afford to be an unpaid intern. All interns must be paid a livable wage, no exceptions.

Solving the systemic racial economic inequality problem does not however solve the second issue of `White Flight', it only adds some diversity to the the flight.

When money leaves a community for newer housing there needs to be an adequate social safety net to prevent the reduction of financial strength in that community from triggering a cascading decline in the community itself. It is my strong suspicion however that the same changes necessary to end systemic racial economic inequality will go a long way towards preventing such a cascading decline.

I strongly recommend that any politicians looking for policy to end our systemic racial economic inequality do extensive reading of the works of the Reverend Dr.\ Martin Luther King Jr.\ and also consult with the Reverend Dr.\ William J.\ Barber \rom{2}.

\subsection{The Sin of Predatory Loans}

Predatory loans are loans that take advantage of the desperation of the borrower for resources to squeeze the borrower into paying far more for the loan than the loan is actually worth. Some predatory loans are illegal but still happen---others are legal.

The most common example of a legal predatory loan is a payday loan. According to CNBC\footnote{\url{https://bit.ly/3v62SPa}} payday loans can have an APR interest rate over 600\%, with Texas being the biggest offender with an APR of 664\%.

With such a high cost for these loans, they are only acquired when the borrower is extremely desperate. The payday loan is a \emph{huge} industry, with an estimated 12 \textbf{million} borrowers each year\footnote{\label{lendedu}\url{https://bit.ly/3bIpXjk}} with a total of more than \money{9000000000} in loan \emph{fees}.

The typical borrower earns less than \money{30000} per year, payday loans are a transfer of wealth from the financially desperate to the already wealthy.

There is a reason why Joe Biden does not want to provide real economic relief to the poor during the pandemic. There is a reason why he promised a public option to the ACA to get elected but then backtracked on that promise\footnote{\url{https://bit.ly/3u79zPF}} and there is a reason why Senator Sinema pranced as she voted against a federal \money{15.00} an hour wage. I beg the people of Arizona to primary her with a socialist in 2024.

Financial desperation is very profitable for their wealthy backers. We the People are being sold out. Under capitalism, the purpose of the middle class is to spend the fruits of the working class to fund the hedonism of the wealthy class. If the working class shrinks, that falls apart. If the working class grows, so does the hedonism of the wealthy class---and that is goal of people like Biden and Sinema. That is where they get their bread and butter.

The typical borrower of a payday loan takes out such a loan to cover the following\footnoteref{lendedu}:

\begin{itemize}
  \item Routine living expenses like gas and groceries
  \item Mortgage payment assistance
  \item Car payments
  \item Credit card payments
  \item Utilities
  \item Financial emergencies
\end{itemize}

From the same source, approximately 58\% of these borrowers are on some kind of government assistance already, including social security. Payday loans thus are a direct theft from what little social safety net our society has.

Payday loans are almost always under \money{1000} indicating that a large percentage of the population (myself included) does not even have \money{1000} in savings or they would just borrow from themselves and avoid the fee. This means an alarmingly large percentage of the population is just a single paycheck away from not being able to make their rent resulting in eviction---a major problem we all witnessed during the 2020 pandemic.

The very fact that such predatory loans exist and are so profitable are a clear sign that many Americans who both have homes \emph{and a job} are on the brink of homelessness.

Why do so many people lack even \money{1000} in savings? I have a better question:

\bigskip

\hl{How the fuck are people being paid less than a livable wage suppose to build up any savings?}

\bigskip

Enact `The Thirty-Five Percent Plan' on page~\pageref{thirtyfive} and the number of payday loans needed will radically drop.

Enact `Benevolence Savings' as described in `Post Office Banking' on page~\pageref{bsavings} and predatory payday loans very well may go away. When there is no demand there is no need for a supply.

\subsection{The Sin of Systemic Racist Land Theft}

I encourage \textbf{\emph{EVERYONE}} to read the following \textsc{ProPublica} article: \textit{``Their Family Bought Land One Generation After Slavery. The Reels Brothers Spent Eight Years in Jail for Refusing to Leave It.''}\footnote{\url{https://bit.ly/3bsGhop}}

\bigskip

Between the years 1910 and 1997, Black Americans lost roughly 90\% of the farmland they owned. Much of that land was land they had rightfully purchased shortly after the civil war.

The method of the initial land theft is often very insidious.

If there is not a will specifying \emph{exactly} who a piece of land goes to upon death of the owner, that land can often be resold to someone else---often developers---without the heirs still living on it even knowing the land they grew up on suddenly belongs to someone else.

One day they are living on land they have every reasonable expectation that it belongs to them and the next day they are told they are trespassing and they end up getting arrested and jailed if they refuse to leave.

I challenge anyone who claims capitalism is a moral economic system to explain why capitalists in America have not only been silent while this blatant land theft takes place---but have directly profited from this blatantly racist theft. And yes, this land theft is blatantly racist. Look at who it has impacted the most---that is no accident.

That land theft through lack of a legal will however is not where the systemic racist crime ends.

In a lot of cases the land had a very low value when it was first purchased. Along the Atlantic coast of the south, for example, much of it was swamp land periodically hit by hurricanes that white people simply did not want. Until now.

Capitalism inherently values the wealthy \emph{regardless of what kind of exploitation was used to gain that wealth} and devalues those in poverty.

Wealthy capitalists come in and steal the land from Black Americans in poverty and then they build their expensive resorts and communities, often devastating the swamp ecology that has been there since long before Columbus set sail. This causes the property value to go up.

The poor Black families that do still own their land and have been living on that land for generations suddenly are faced with excessive property taxes they simply can not afford and are left with two choices: Sell for a low-ball price to a wealthy developer or lose their land because they can not afford the tax payment.

Do you think they have representation in government or do you think they are being taxed without representation?

Clearly it is the latter and immediate action is required.

Congress needs to put an immediate halt to land theft that results from a lack of paperwork declaring an heir and serious reparations are needed. And I do mean serious reparations, not just token gestures like Pelosi leading other millionaires in the wearing of Kente cloths as a publicity stunt intended to make rich white liberals feel warm and fuzzy inside.

The taxes on generational land should \emph{never} increase just because rich developers acquired adjacent land and built resorts and housing for the rich on it. That is seriously fucked up gentrification taken to the extreme.

Anyone in government who claims to support the Black Lives Matter movement but is not working to right this horrible wrong that the largely white capitalist oligarchy governing this nation has committed against these Black Americans is both a fraud and a liar.

Read the \textsc{ProPublica} article. Please.

And note that Mark Zuckerberg is using a similar tactic to steal generational land in Hawaii\footnote{\url{https://bit.ly/2SMGps5}}. Capitalists continually demonstrate they are pure evil.
