\phantomsection
\addcontentsline{toc}{section}{Mus Musings}

\begin{abstract}

\noindent I thought about being the `Ramen Shaman' because I eat a lot of Ramen but Jake Angeli messed that up\ldots{} (joke)

This manifesto is partly a description of the problem, partly a suggestion to solutions, and partly an expression of extreme frustration and anger.

I was taught something called the `Sandwich method' where you say something positive about someone before a criticism and then followed by something positive. I have found that method is only really productive at making the other person feel good about themselves---they eagerly soak up the bread and blissfully ignore the meat.

Maybe the sandwich method helps neurodivergents avoid conflict in the business meeting but it does not actually solve the problem the neurodivergent often so accurately sees. It is time for the politicians of this country to wake up and realize the criticisms are not just a lack of social graces, the criticism are extremely valid and the problems our politicians perpetuate are literally killing people\footurl{https://bit.ly/3bHabp4}.

The primary intent of this manifesto is to get problems solved. Talking about them is not good enough. Action is required. We did not fix anthropomorphic climate change by talking about it, and politicians did an awful lot of talking about it my entire life. Actual action to fix it was never taken.

When I present solutions, I doubt there are very many people who will agree with all of them. Quite possibly the disagreement are valid---but lack of action because of disagreement is the action of a coward. Take action actually designed to work even if it isn't my solution.

On more than one occasion I will give biblical references. Whether or not you are religious, and if you are religious then whether or not that religion is Christianity or even an Abrahamic religion, there is still wisdom to be found in the Bible. In point of fact, much of the wisdom that can be found in the Bible can also be found in the religious texts of other religions and in non-religious texts. The Bible just happens to be what I know best, I was taught to read it for comfort and with the current state of things---that means I read it an awful lot. Other forms of self care to deal with my frequent depression I simply can not afford.

I want to make it abundantly clear that when I refer to myself as the `Anymouse Prophet', this is not a claim to religious authority.

A religious prophet is one who is shown a glimpse of the world from the perspective of God. One could say they are able to empathize with the will of God, what God wants for his creation.

I make no such claim. No vision came to me, an angel of the \textsc{Lord} did not come to me, this did not come from prayer and fasting. I empathize with those our society has trodden upon, cast out, and rejected. Those that are viewed as vermin---rodents that are seen as pests by the wealthy just for their want of something to eat and a place to sleep.

If the Jesus of the Bible is to be believed, they are who the God of the Bible empathizes with as well, so perhaps in that small way I am a prophet in the traditional sense. However it still needs to be made very clear that I claim absolutely no religious or divine authority and I \emph{vehemently reject} the authority of organized religion.

I read an interesting story about a German Lutheran missionary to China named Georg Kohls (pronounced differently than George). In 1938 in Guangzhou, he led a prayer without mentioning Hitler. He was chastised for it with the criticism `{``}people like Herr Kohls, who not even once mention the \textit{F\"{u}hrer}, and surely never prayed for him,'' who helped contribute to the fragmented political situation in Germany.'\footbib{From Christ to Confucius}{Albert Monshan Wu}{page 261}{2016}{Yale University Press}{978-0-300-21707-0}

His continued refusal to give support to Hitler or the Nazi Party caused a rift to develop between him and those above him in the organization but he understood who Hitler was and he refused the authority of the very organized religion he was part of when it came to matters of politics. History clearly shows he was right to do so---if only more German Lutherans had done so!

\bigskip

What if God was one of us? Just a slob like one of us? Just a stranger on the bus? Tryin' to make his way home. Would organized religion help him? Or would organized religion blame his hardships on the sins and choices they are sure he must have made to be in such a desperate position? Organized religion always leads to the seeking of power for the sake of power, even when the religious organization started with good intentions. I will not go down that path, even though it would be easier for this manifesto to gather a following if I did claim religious authority with an organized religion behind it. Always remember, Jesus rejected the organized religion of his day. \hl{True religion in the sight of our \textsc{Lord} is this: to visit orphans and widows in their distress, and to keep oneself unstained by the hedonism of capitalism.}

\bigskip

For the many in this country who do crave religious authority, consider this: It wasn't the wealthy that God called out of Egypt to make into his people in a land of promise and blessing. It was the slaves who were oppressed by the wealthy---they are who God called out of Egypt. After calling them out of Egypt, God demanded of them that their blessing not be used to make them wealthy oppressors themselves, but God specifically demanded of them that they use their blessing to show compassion and kindness to the poor and the foreigners in their land, remembering that they were once oppressed foreigners themselves. The justice God required of them is detailed in Exodus 23:1--9 amongst many other places that modern Evangelical Capitalists and the current nation of Israel do not like to read.

For the many in this country who do crave religious authority, consider this: Sodom was not destroyed because of butt sex. The prophet Ezekiel, an actual Prophet in the traditional sense, tells us \emph{exactly} why Sodom was destroyed:

\begin{quote}
Now this was the sin of your sister Sodom: Her people were arrogant, voracious, and without empathy---they refused to help the poor and those in need. They were haughty and did what is wicked in my sight. So I destroyed them as you have seen.
\end{quote}

Under capitalism, the United States of America has become like Sodom, and Evangelical Capitalists dare to use the name of the \textsc{Lord} in vanity as they proclaim it is God's will that we have become like Sodom.

In the interest of pedantic fairness, I do have to concede the United States is not \emph{exactly} like Sodom when it was destroyed. Matt Gaetz likely would have accepted the disgustingly offensive offer of Lot's daughters.

\bigskip

Just as Evangelical Capitalists reject the social justice message of Moses, the social justice message of Ezekiel, and the social justice message of Jesus, they also reject the social justice message of Frederick Douglass, the social justice message of the Reverend Dr.\ Martin Luther King Jr., and they will reject this social justice message. For to them, social justice is of the devil and is `evil communism'. If the poor do not exist to make the rich even wealthier, then the poor have no purpose and are to be condemned. These people will call me a socialist as a slur. Whether or not I am an \emph{actual} socialist is a matter of academic debate.

I do consider myself a socialist but many socialists reject me as one of them. That is okay, I do not require their acceptance for me to value their input and viewpoints on many aspects of a fair and just society.

The major deviation I have from `traditional socialism' (Marxist Socialism) is that I do not believe socialism should be defined as the workers owning the means to production. I believe that is a \emph{result} of socialism that will happen naturally, but for me, that definition of socialism has the danger of being ableist---those who have physical or mental disabilities such that they are not able to participate in the production of goods can be left out. That is a danger the definition of socialism should explicitly address.

I am definitely not a communist. To me, autonomy is critically important. Autonomy requires privacy and privacy requires private property as an inherent right---whether it is intellectual property or physical property. It is my view that both communism and capitalism lead to the loss of the fundamental inherent human right to privacy for the vast majority of the population (Exhibit A: Google Trackers. Exhibit B: Facebook Trackers. Exhibit C: Amazon Trackers. Exhibit D: Border Patrol buying phone geo-location tracking data so they can dump the water kind people left for Jesus to find when Jesus comes up through the desert into the promised land escaping the bondage of Egypt) and as such, both communism and capitalism lead to a loss of autonomy which leads to a fascist/authoritarian oligarchy.

How then do I define socialism? To me, \hl{socialism is an economic system that gives higher priority to the human dignity \emph{and autonomy} of the least among us than it gives to the prosperity and property of the wealthy}. This is in stark contrast to capitalism where priority is given to the prosperity and property of the wealthy over the human dignity and autonomy of the least among us.

What I phrase as `Evangelical Capitalism' is the abuse of the dominant organized religion in the United States of America as a propaganda tool to support capitalism \emph{despite} the explicit biblical passages stating that the love of money is at the root of all that is evil and that the wealthy should redistribute their wealth to the poor. Evangelical Capitalism is the abuse of religion to support an economic system that leads to fascism, an economic system that prioritizes the wealth and property of a few elect over the human dignity and autonomy of all. While on the the topic of Evangelical Capitalists---I seem to remember Jesus saying something about the least among us\ldots{} maybe towards the end of Matthew 25?

It is Evangelical Capitalists who proclaimed Trump to be God's anointed (a messiah) and then worshiped a golden idol of Trump at the 2021 Conservative Political Action Conference (CPAC). I call it out not because I am opposed to the religious freedom of Evangelicals, but because I believe as a political movement, Evangelical Capitalism is the biggest danger to freedom the United States of America has ever seen. Remember Ashburton House and Lafayette Square on June 1st, 2020. Let the reader understand\footurl{https://bit.ly/3uILD6t}.

It is no coincidence that just like members of Al-Qaeda and just like members of ISIS---prominent members of the Evangelical Capitalist movement like Lauren Boebert, Marjorie Taylor Greene, and Donald Trump Jr.\ like to pose for photographs with an arsenal of intimidating guns.

Those who crave religious authority should not listen to the leaders of the Evangelical movement. They should read Proverbs 6:16--19\footurl{https://bit.ly/3v8kjPg} and think about people like the Trump family and Hawley and Boebert and Greene and Cruz as they read it.

Evangelical Capitalism is far more dangerous to American freedom than any domestic \emph{or foreign} threat has ever been, with the noted exception of the threat and damage that Manifest Destiny (also a tyranny justified by religious zeal\footurl{https://bit.ly/3bEIs8v}) imposed with the genocide of the Indigenous Peoples.

As an example of my distinction between socialism and capitalism: In the United States of America, health care is a capitalist for profit industry. It exists on the premise that profit is needed to drive innovation in medicine, and that premise---despite lack of any academic research to validate it---is sold to the masses as a reason why our health care should remain a for profit industry. As a result, people in America have literally died because they have had to self-ration their insulin shots, a drug that is cheap to manufacture but is only provided based upon the profit it brings to the pharmaceutical companies rather than based upon the need of the patient to survive.

\begin{quote}
I don't believe the Devil, I don't believe his book---but the truth is not the same without the lies he made up. I don't believe it when they tell me, there ain't no cure---the rich stay healthy, the sick stay poor.
\end{quote}

In Cuba where health care is socialized, on the other hand, they developed a vaccine that is both cheap to manufacture and effective at preventing lung cancer\footurl{https://bit.ly/33D1GXx}. This vaccine is now used in several countries with socialized medicine but the capitalist pharmaceutical industry in the United States has shown little interest in it. Under capitalism where prosperity and property take priority, it is far more profitable to treat lung cancer with expensive proprietary drugs than it is to use an inexpensive vaccine to prevent the disease in the first place.

A capitalist judges the health of the economy by the Gross Domestic Product (GDP) and the stock market. Such measurement is conceptually flawed, it leads to the health of the economy being judged on statistical outliers---like it was during the so-called `Roaring 20s'---and like it is now. A socialist on the other hand judges the health of the economy by the housing security, food security, and opportunity of class mobility of the poorest 10\% of the population.

A key aspect to the definition of socialism that I prefer is autonomy and self-determination. Housing security is part of autonomy and is what this manifesto addresses, but it is not the only part of autonomy. Food security, health security, meaningful education, and a democratic voice in government are all critical components of autonomy and self-determination.

A democratic voice in government means an end to voter suppression.

As far as I can tell, Stacey Abrams is neither a socialist by any published definition nor does she claim to be one, but her incredible work in Georgia to overcome voter suppression is exactly what is required to end voter suppression and is thus compatible with socialist goals.

Despite the mainstream media claims, Georgia did not `flip blue' in 2020. Using the false dichotomy of `red' and `blue' states, Georgia has actually been a `blue state' for quite some time. In the recent past, it `votes red' not because that is how the people of that state align themselves---but rather---because the voice of minorities has long been suppressed in that state. The fact that Republicans in that state are trying to pass even more suppressive voter laws in the wake of the 2020 election is a clear indication that voter suppression for Republicans is an acceptable tool to use to keep power, a clear sign of fascist ideals.

Here in my home state of California, gun control advocates wanted to use the `Real ID' act to control who could buy guns or ammunition, requiring a `Real ID' for the purchase of either. Republicans rightfully claimed that violated their constitutional right to bear arms, a `Real ID' being difficult for many legal citizens to obtain. Yet at the same time, that `Real ID' is exactly what many of \emph{these same Republicans} want to require of us to be allowed to vote.

The constitutional right to bear arms is holy to them and should not be denied from anyone. The constitutional right to vote---they don't give a rats ass about preserving that right. The hypocrisy of it is quite mind boggling.

Stacey Abrams and many others are working very hard to overcome voter suppression, and we must applaud and support those efforts even when their personal politics do not necessarily align with ours. An actual Democracy means \emph{everyone} has a voice in government, whether or not their voice agrees with ours.

To that end, I ask my fellow socialists to avoid the extreme political polarity that has plagued both major parties in the country over the last three or four decades. At one point in time, a typical member of congress would vote with their party more than half the time but less than \sfrac{3}{4} of the time. Unfortunately those days are gone, and with those days gone, Americans in general have less of a voice in government. When Republicans are in power, the voices of those who align with Democrats are silenced. When Democrats are in power, the voices of those who align with Republicans are silenced. This is not a healthy democratic environment, this is an environment that leads to fascism, regardless of which party has control.

As socialists, we need to fight for real democracy, the kind of democracy this nation claims to have but never have we actually had. We need the kind of democracy that our great socialist visionaries like the Reverend Dr.\ Martin Luther King Jr.\ dreamed of. When we have that kind of a democracy, I do believe socialism will follow. The wealthiest of the wealthy will leave this country, and we will be better off without their poison.

So please, do not fight against those like Stacey Abrams who fight to bring about the democracy we so desperately need. Even when their views do not represent us, their views do represent someone. When we have a true democracy, socialist views will prevail. Do fight against those who seek to suppress the vote, that is a battle we can not afford to continue to lose.

Stacey Abrams very well may disagree with some of the solutions presented here---as is her inherent constitutional right---but I guarantee many of the suppressed voters she helped bring to the polls will be in agreement.

Donald Trump seriously tarnished the value of the Presidential Medal of Freedom when he awarded it to Limbaugh. Joe Biden can restore honor to that medal by awarding it to Stacey Abrams for her work in overcoming voter suppression.

If we can shift this nation away from partisan politics and towards politics that serve the people instead of party, then we can get at least part of the socialist agenda into law even with only a minority representation in government. Democracy is key to this happening. As socialists, we need to work towards overcoming voter suppression with any politician who is committed to doing so, whether or not they bear the red rose.

Convince the people that socialism is the answer and politicians that align with socialism will be elected---as long as the vote of the people is not suppressed.

\noindent\rule{7cm}{0.4pt}

\bigskip

I have a confession to make. Part of this manifesto is driven by fear. The United States of America no longer functions as a Democratic Republic, the checks and balances have been destroyed.

To anyone who is not willfully ignorant, it is clear the impeachment process put into the Constitution to check the power of the President no longer functions. With both of the previous two impeachment trials, it was made clear beyond reasonable doubt that pseudo-President Trump needed to be removed yet that did not happen.

In the Brett Kavanaugh confirmation hearing, you would have to be a blithering idiot to think `FFFF' was just making fun of a friend with a lisp and you would have to be a blithering idiot to believe that ``Devil's Triangle'' referred to a drinking game. We thus have one confirmed Supreme Court justice who thought it was okay to tell complete fabrications to the Senate confirmation hearing and we have Senators who thought it okay that he told lies to them. And we have the wife of another Supreme Court justice who literally funded insurrectionists traveling to the Capitol in an attempt to overthrow the election process.

Our constitutional checks and balances simply no longer function.

\bigskip

In Georgia, thanks to the very hard work of people like Stacey Abrams, voter suppression was overcome and many who previously did not have a voice were finally given a voice. And how does the Georgia state government respond? Instead of celebrating the voice of those finally being heard---they passed a bunch of suppressive laws trying to silence those voices once more in the future.

I will be in Georgia in 2022 passing out food and water and if I am arrested for it, God will rain down hell-fire on Georgia.

I invite anyone who is able to cast a mail-in ballot in their own state to join me in Georgia (or elsewhere) in providing water and snacks to those waiting in line to vote. Do not try to sway their vote, but do pass out food and water and come between them and the fascists who may be there to intimidate the voters. If the police arrest and harass us, they aren't arresting or harassing those waiting in line to vote. But pray for peace at the elections, that is the best outcome.

With the failed state of our Democratic Republic, armed revolution is unfortunately a very real possibility and with an armed revolution there is always a lot of pain and death which is often followed by very dark times once the revolution is over.

Things are very scary right now.

The only way I see out of it is if we can transition to socialism and take power away from the oligarchy politically \emph{before} the armed revolution happens. I do not want the streets to flow with blood.

For those who seek religious authority, consider \amprom{2} Chronicles 7:14:

\begin{quote}
\textbf{If} my people who are called by my name humble themselves, pray, seek my face, and turn from their wicked ways, \textbf{then} I will hear from heaven, and will forgive their sin and heal their land.
\end{quote}

\noindent In computer science that is what they call a conditional \texttt{if-then} statement. The \texttt{then} part of the statement can only happen if the conditions of the \texttt{if} part of the statement are met.

The Evangelical Capitalists dare to ask God to bless us, but they do not do the very things their Bible specifically says must happen for that blessing to come.

Instead they worship a golden statue of Trump erected at CPAC and they worship guns designed to kill lots of people in a short of amount of time instead of wanting those guns turned into plowshares and they cheerfully support the exploitation of the poor both at home and abroad just to make the wealthy even wealthier, completing ignoring the prayers of Job where he says he should lose his arms for such things\footurl{https://bit.ly/3eIPCdO}.

Note that forgiveness of sin is also part of the \texttt{then} clause that depends upon the \texttt{if} conditional. These Evangelical Capitalists lie to themselves when they claim to be forgiven yet willfully continue in their wicked ways.

I want things to change, and this manifesto is a road map for how that can happen in the housing market.

If things do not change, very dark times are ahead.

If things do not change, America is as fucked as Sodom.

\bigskip

---The Anymouse Prophet



\end{abstract}
