\section{No Taxation Without Representation}

\epigraph{``This is something I've been seeing for a long time. Rich people in this country only interact with other rich people. They live in gated communities, eat at restricted restaurants, and spend thousands on a watch.\\[1\baselineskip] They really have no reference for how Americans live.''}{\textit{@DPurdyJackson \\ Twitter---May 06, 2021}}

\bigskip

\noindent Tax rates are set by the `Ways and Means' committee which sends it to the House of Representatives which---upon their approval---sends it to the Senate for final approval.

In both houses, most representative make \money{174000} a year. This is \emph{before} all the income they earn from their conflict of interest investments. According to OpenSecrets.org\footnote{\url{https://bit.ly/33vPtDV}} over half of them are millionaires. According to Google, only 8--9\% of Americans in general are millionaires.

Those making poverty wages simply do not have adequate representation in government and therefore---as our founding fathers made very clear---should not be subject to taxation. Those who disagree are `Loyalists' and not `Patriots' by 1770s Boston standards.

I propose that federal taxation does not begin until income is at least 10\% higher than minimum wage in the most expensive place to live.

Let $G$ represent gross annual income and let $W$ represent the highest minimum wage as calculated by the The Thirty-Five Percent Plan (see page \pageref{thirtyfive}). Then the following formula defines the cut-off income for which no taxes are owed at the federal level:

\[
G = 1.10 \times (12 \times 21 \times 8 \times W)
\]

If $W$ ends up being, say, \money{30.00} an hour which is a very likely possibility, then the starting gross income for federal income tax would thus be:

\[
G = 1.10 \times (12 \times 21 \times 8 \times \money{30.00}) = \SI[group-separator={,}]{66528}[\$]{\per\year}
\]

I applaud CEO Dan Price. He set the minimum wage of his Seattle company to \money{70000} per year, very close to the the number produced above---Seattle being one of the places likely to have a \money{30.00} an hour minimum wage using `The Thirty-Five Percent Plan'. I do not not know how he came to that figure but it is very congruent with what my manifesto asks.

Note the median income in the United States in 2019 was \money{31133} per year. The majority of Americans do in fact live in poverty, just like they did in the so-called `Roaring 20s' that resulted in the Great Depression. The financially privileged---including members of both houses of Congress---are shielded from the very real poverty in America. They do not see it, they do not \emph{want} to see it.

To compensate for the taxes the United States Treasury loses from no longer being able to tax those in poverty---levy more aggressive progressive taxes on the wealthy like we did after the Great Depression---and close the incredible number of tax loopholes.

Companies like Uber (one of many) who purposefully rob the treasury\footnote{\url{https://bit.ly/3eI4I3a}} need to be prosecuted into oblivion. Dara Khosrowshahi and CEOs like him belong in federal prison. They are thugs that are no different than Al Capone. The apathy of Khosrowshahi towards the brutal murder of Jamal Khashoggi makes that extremely clear---life has little actual value to him.

This country should be funded by those with excess, not by those who are starving.

\subsection{Systemic Racism in Land Theft and Property Tax}

I encourage \textbf{\emph{EVERYONE}} to read the following \textsc{ProPublica} article: \textit{``Their Family Bought Land One Generation After Slavery. The Reels Brothers Spent Eight Years in Jail for Refusing to Leave It.''}\footnote{\url{https://bit.ly/3bsGhop}}

\bigskip

Between the years 1910 and 1997, Black Americans lost roughly 90\% of the farmland they owned. Much of that land was land they had rightfully purchased shortly after the civil war.

The method of the initial land theft is often very insidious.

If there is not a will specifying \emph{exactly} who a piece of land goes to upon death of the owner, that land can often be resold to someone else---often developers---without the heirs still living on it even knowing the land they grew up on suddenly belongs to someone else.

One day they are living on land they have every reasonable expectation that it belongs to them and the next day they are told they are trespassing and they end up getting arrested and jailed if they refuse to leave.

I challenge anyone who claims capitalism is a moral economic system to explain why capitalists in America have not only been silent while this blatant land theft takes place---but have directly profited from this blatantly racist theft. And yes, this land theft is blatantly racist. Look at who it has impacted the most---that is no accident.

That land theft through lack of a legal will however is not where the systemic racist crime ends.

In a lot of cases the land had a very low value when it was first purchased. Along the Atlantic coast of the south, for example, much of it was swamp land periodically hit by hurricanes that white people simply did not want. Until now.

Capitalism inherently values the wealthy \emph{regardless of what kind of exploitation was used to gain that wealth} and devalues those in poverty.

Wealthy capitalists come in and steal the land from Black Americans in poverty and then they build their expensive resorts and communities, often devastating the swamp ecology that has been there since long before Columbus set sail. This causes the property value to go up.

The poor Black families that do still own their land and have been living on that land for generations suddenly are faced with excessive property taxes they simply can not afford and are left with two choices: Sell for a low-ball price to a wealthy developer or lose their land because they can not afford the tax payment.

Do you think they have representation in government or do you think they are being taxed without representation?

Clearly it is the latter and immediate action is required.

Congress needs to put an immediate halt to land theft that results from a lack of paperwork declaring an heir and serious reparations are needed. And I do mean serious reparations, not just token gestures like Pelosi leading other millionaires in the wearing of Kente cloths as a publicity stunt intended to make rich white liberals feel warm and fuzzy inside.

The taxes on generational land should \emph{never} increase just because rich developers acquired adjacent land and built resorts and housing for the rich on it. That is seriously fucked up gentrification taken to the extreme.

Anyone in government who claims to support the Black Lives Matter movement but is not working to right this horrible wrong the largely white capitalist oligarchy that is governing this nation has committed against these Black Americans is both a fraud and a liar.

Read the \textsc{ProPublica} article. Please.

And note that Mark Zuckerberg is using a similar tactic to steal generational land in Hawaii\footnote{\url{https://bit.ly/2SMGps5}}. Capitalists---with a very few exceptions---continually demonstrate they are pure evil.
