\section{Medicare For All}

Medicare For All does not seem to be \emph{directly} related to the solving the housing crisis yet it actually is.

\bigskip

In 2008, medical debt was a leading cause of personal bankruptcies.

\bigskip

In 2009, medical debt was a leading cause of personal bankruptcies.

\bigskip

In 2010 the `Affordable Care Act' (ACA) passed. Note the word `Affordable'. Also please note that `Affordable' is a term that is very relative to one's economic class.

\bigskip

In 2010, medical debt was a leading cause of personal bankruptcies.

\bigskip

In 2011, medical debt was a leading cause of personal bankruptcies.

\bigskip

In 2012, medical debt was a leading cause of personal bankruptcies.

\bigskip

In 2013, medical debt was a leading cause of personal bankruptcies.

\bigskip

In 2014, medical debt was a leading cause of personal bankruptcies.

\bigskip

In 2015, medical debt was a leading cause of personal bankruptcies.

\bigskip

In 2016, medical debt was a leading cause of personal bankruptcies.

\bigskip

In 2017, medical debt was a leading cause of personal bankruptcies.

\bigskip

In 2018, medical debt was a leading cause of personal bankruptcies.

\bigskip

In 2019, medical debt was a leading cause of personal bankruptcies.

\bigskip

In 2020, medical debt was a leading cause of personal bankruptcies.

\bigskip

As a neurodivergent I often see patterns others fail to see. That pattern however is hopefully very clear. Both before and after the ACA passed, medical debt has been a leading cause of bankruptcies. In fact for many if not all of the years mentioned, it was \emph{the} leading cause of personal bankruptcy. It was just too depressing for me to research which was `the' leading cause every single year, so I stopped after it was clear it was the majority of them\footnote{\url{https://bit.ly/3eJh1fF}}.

A flaw I have noticed with neurotypicals within the species \textit{Homo sapiens sapiens}---they have a tendency to look at the anecdotal cases that match their desired outcome rather than attempting to look at the big picture. In other words, neurotypicals have a strong tendency for what is known as `Confirmation Bias\footnote{\url{https://bit.ly/2Rk5nPb}}'.

This is what has happened with the ACA. Liberals really wanted it work, they wanted it to work so badly that they look at the few cases where it does in fact help people and they use those cases to proclaim it is a success \emph{without} looking at the bigger picture. Bankruptcies that result from medical debt is a pretty obvious way to get a grasp of the bigger picture but that is ignored by those who continue to advocate for the ACA. Bankruptcies that result from medical debt make it very clear that the `Affordable' in ACA is a failed goal.

The ACA is clearly a failed experiment. For far too many people it simply does not work. The ACA reminds me of a phrase we use to say as a child when playing cops and robbers: `Your money or your life.'

Politicians \textbf{INCLUDING JOE BIDEN} need to stop listening to the wealthy who profit from the ACA. It needs to be replaced with Medicare For All.

\epigraph{``It would be an insult to my dead son for everyone to have health care.''}{\textit{Joe Biden \\ Campaign Ad---August 27, 2019}}

Joe Biden needs to understand that as a leader, policy decisions should be based upon what is best for the American People---ALL of the American People.

Emotions are frequently not rational. To base a policy position on an emotion related to a deceased relative rather than based upon logic is an insult to the American People and if Joe Biden can not understand that, he is not fit to be our President. Perhaps he is not as disastrous as who he replaced, but he is still not fit to be our President.

Causes of homelessness are complex and varied. Filing for bankruptcy often \emph{prevents} homelessness. However those who do need to file for bankruptcy are clearly in a financial situation where even with a successful bankruptcy, they are far more likely to become homeless.

The ACA does not fix the problem. We need Medicare For All and we need it now.
