\section{Homeless Veterans}

Some startling statistics from the National Coalition of Homeless Veterans\footurl{https://bit.ly/3v1oQ61}:

\begin{itemize}
  \item 11\% of homeless adults are veterans. This is statistically significantly higher than the general population of adults.
  \item 51\% of homeless veterans have a disability.
  \item 50\% of homeless veterans are 51 or older. This is statistically significantly higher than the general population of homeless adults.
  \item 45\% (roughly) of homeless veterans are African American or Hispanic. This is statistically significantly \emph{much} higher than the general population. Yet when you see photos of homeless veterans in news stories, they are almost always are shown as white (for example the EndHomelessness.org page on veterans\footurl{https://bit.ly/3fsigid}).
\end{itemize}

It is abundantly clear that being a veteran increases your odds of ending up homeless. This is statistically even greater if you are Hispanic or Black, though I would caution the reader not to fall into the trap of equating statistical correlation to cause and effect. A possible explanation is that Hispanic and Black soldiers are more likely to have a lower education level than white soldiers resulting in them being more likely to be in units where Post-Traumatic Stress Disorder (PTSD) will be a contributing factor \emph{and} are less likely to have gainful employment opportunities when they exit the military. I simply do not know the reason for that statistic but it should be investigated.

What I do know is that serving in the military increases the odds of homelessness and a large factor---though not the only factor---is PTSD from combat.

The United States of America likes to go to war.

In a few cases, such as World War \amprom{2}, war may in fact be justified. In the vast majority of cases, I do not believe it is. We go to war because of Capitalist Imperialism. It makes some people very wealthy even though things like bone spurs prevents them from ever having gone to war themselves.

This must end. It is blood money. It is wealthy capitalists securing more money by sending those in poverty to die.

Radically reduce the number of wars we become involved in and we radically reduce the number of homeless veterans. Radically reduce the number of wars we become involved in and we free up trillions of dollars to invest here at home.

Our military industrial complex is evil.
